Performance of two different ontological and data access methods

### 2014-07-03 cold2014/magnus.tex
remove screenshot entirely
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@720 43ef1190-90fd-4dd7-a769-d0121f02b80e

The application present users with a web interface where they can
input values for any specification they might want to search for.  In
Figure \ref{initialView} we can see how the application initially
looks for a user. Here the user can input values for the different
specifications, for instance fuel type or CO$_2$ emission. After a
user is done choosing specifications he can execute the actual car
model search. The application extracts the data from the form and
comprises it into another format that can easily be used later on. The
next step begins in the search module. Here it starts a thread for
each possible car model to execute each individual search. In the end
the user is presented with a set of valid models to choose from, which
contain the chosen specifications. In Figure \ref{afterSearch}, we
can see what the user is presented with after a successful query
execution, in this case seventeen different models. In this run, the
user have searched for a model with diesel fuel, automatic
transmission, four or more gears and a maximum of six seats. We also
have the values and URIs for each of these valid models, which means
that the application could present the user with more information than
it does today.

\begin{figure}
  \centering
      \includegraphics[width=12cm]{afterSearch.png}
  \caption{The view after a search}\label{afterSearch}
\end{figure}
There are done some pre-computations to make the application a little
more effective. This includes extracting all the model names from both
ontologies, initiate all possible partially defined products as a
PartialCar object and creating some internal structure. These
pre-computations were done so that it would be possible to present the
user with the name of each car model, not just the URI. We will also
describe more in depth how the car model search is done later on.

>>>>

The application present users with a web interface where they can
input values for any specification they might want to search for.  In
Figure \ref{initialView} we can see how the application initially
looks for a user. Here the user can input values for the different
specifications, for instance fuel type or CO$_2$ emission. After a
user is done choosing specifications he can execute the actual car
model search. The application extracts the data from the form and
comprises it into another format that can easily be used later on. The
next step begins in the search module. Here it starts a thread for
each possible car model to execute each individual search. In the end
the user is presented with a set of valid models to choose from, which
contain the chosen specifications, e.g. the user have searched for a
model with diesel fuel, automatic transmission, four or more gears and
a maximum of six seats.

There are done some pre-computations to make the application a little
more effective. This includes extracting all the model names from both
ontologies, initiate all possible partially defined products as a
PartialCar object and creating some internal structure. These
pre-computations were done so that it would be possible to present the
user with the name of each car model, not just the URI. We will also
describe more in depth how the car model search is done later on.
